### 2016-09-29 rebuttal.tex

\question Line 355, add a sentence explaining that in SymPy \texttt{str == repr}, because in Python \texttt{repr} is used to get an unambiguous valid Python code representation, while the return value of \texttt{str} is meant to be human-readable.
\begin{solution}
See the added footnote~\ref{P-note:repr}.
\end{solution}

\question Lines 359 and 379: what is 2D text representation? It seems that ``2D'' shouldn't be here.
\begin{solution}
This sentence was replaced with:
\begin{quote}
A two-dimensional (2D) textual representation of the expression can
be printed with monospace fonts via \verb|pprint|.
\end{quote}
We use here the same terminology as in the Mathematica
online documentation, e.g., the
\href{https://reference.wolfram.com/language/ref/OutputForm.html}{\texttt{OutputForm}}
function:
\begin{quote}
\texttt{OutputForm[expr]}: prints as a two-dimensional representation of expr using only keyboard characters.
\end{quote}
\end{solution}

\question Line 427: every dictionary is a ``dictionary of keys''. This should be a dictionary with coordinate tuples as keys associated with the appropriate values.
\begin{solution}
``Dictionary of Keys'' (DOK) refers specifically to a sparse matrix
representation where entries are stored as \texttt{(row, column)} pairs
mapping to the elements. See for instance \texttt{scipy.sparse.dok\_sparse}. We
have fixed the capitalization of ``Dictionary of Keys'' and added the
abbreviation (DOK), and stated explicitly what is meant by this. We have also
made a similar note about List of Lists (LIL) earlier in the section.
\end{solution}

\question Section 4 would benefit from an introduction, and lines 440-- should become a new subsection 4.1. (named ``Float'' or ``Real numbers support'' or similar).
\begin{solution}
We have added an introduction and a subsection~\ref{P-sec:floating-point}, ``Floating-Point Numbers''
(which, for mathematical clarity, we consider to be distinct from ``real
numbers'').
\end{solution}

### 2016-09-29 numerics.tex
Cross reference the floating point section in the rebuttal

\subsection{Floating-Point Numbers}
Floating-point numbers in SymPy are implemented by the \texttt{Float} class,
which represents an arbitrary-precision binary floating-point number by
storing its value and precision (in bits). This representation is distinct
from the Python built-in \texttt{float} type, which is a wrapper around
machine \texttt{double} types and uses a fixed precision (53-bit).

>>>>

\subsection{Floating-Point Numbers}
\label{sec:floating-point}
Floating-point numbers in SymPy are implemented by the \texttt{Float} class,
which represents an arbitrary-precision binary floating-point number by
storing its value and precision (in bits). This representation is distinct
from the Python built-in \texttt{float} type, which is a wrapper around
machine \texttt{double} types and uses a fixed precision (53-bit).
